Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 Discussion.tex

\subsubsection{Discrete Preferences}
Discrete preferences by agents are captured by the following assumption (which states that the agents who are close to tied between two arms have measure 0):

>>>>

\subsubsection{Discrete Preferences}
\label{subsec:discrete}
Discrete preferences by agents are captured by the following assumption (which states that the agents who are close to tied between two arms have measure 0):
